%Document details
\documentclass[titlepage, table]{article}
\title{Asset Allocation - Investment Advice to Best Pensions}    %Fag og opgave nr.
\author{Anders Bang and Andreas Poulsen (fjr422, zmh741)}
\date{\today}
%Dato

%Packages
\usepackage[utf8]{inputenc}
\usepackage[autostyle=true]{csquotes}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{bbm}
\usepackage[danish, english]{babel}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{dsfont}
\usepackage{fancyhdr}
\usepackage{mathtools}
\usepackage{lastpage}
\usepackage{hyperref} % Skal man kunne klikke på referencer?
\usepackage{caption}
\usepackage{lipsum}
\usepackage{multirow}
\usepackage[export]{adjustbox}
\usepackage{physics}
\usepackage{algpseudocode} %pseudocode
\usepackage{algorithm}
\usepackage{adjustbox} % to rotate tables

%Set up the page
\usepackage[top=2.5 cm, bottom= 2.5 cm, textwidth=480 pt]{geometry}
%\usepackage[a4paper, top=2.5, bottom=2.5]{geometry}
 %\geometry{
 %a4paper,
 %total={170mm,257mm},
 %left=20mm,
 %top=20mm
 %}
 \linespread{1.15}

\pagestyle{fancy}
\fancypagestyle{plain}{}
\fancyhf{}

\renewcommand{\footrulewidth}{0.4pt} %Linje i bunden?

%\setlength{\headheight}{30pt}  % Increase the header height
%\setlength{\headsep}{25pt}  

%Header and footer
\rhead{\today}                      %Dato
\chead{Asset Allocation - Investment Advice to Best Pensions}                %Fag og nr.
\lhead{fjr422, zmh741}                    %Forfatter
\rfoot{Page \textbf{\thepage}}

%Declaring commands
%\DeclareMathSymbol{*}{\mathbin}{symbols}{"01}

\newcommand{\indep}{\perp \!\!\! \perp} %Independent

\newcommand{\N}{\mathbb{N}} %Natural numbers
\newcommand{\E}{\mathbb{E}} %Expectation E
\newcommand{\A}{\mathcal{A}} %Caligrafic A (Inf. Gen.)
\newcommand{\G}{\mathcal{G}} 
\newcommand{\F}{\mathcal{F}}
\newcommand{\R}{\mathbb{R}} %Real numbers
\newcommand{\C}{\mathbb{C}} %Complex numbers
\renewcommand{\P}{\mathbb{P}} %Probability P
\renewcommand{\L}{\mathcal{L}}
\renewcommand{\E}[1]{\mathbb{E}\left[ #1 \right]} %Expectation
\newcommand{\V}{\mathcal{V}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\cov}[1]{\text{Cov}\left( #1 \right)} %covariance
\renewcommand{\var}[1]{\text{Var}\left( #1 \right)} %Variance
\newcommand{\inprod}[1]{\left\langle #1 \right\rangle} %Inner product
\newcommand{\assim}{\overset{a.s.}{\sim}} %asymptotic similar
\newcommand{\normal}[2]{\mathcal{N}\left( #1 , #2  \right)} %Normal Distribution
\newcommand{\asto}{\overset{a.s.}{\to}} %Converge almost-surely
\newcommand{\pto}{\overset{\mathbb{P}}{\to}} %Converge in Probability
\newcommand{\dto}{\overset{d}{\to}} %Converge in distribution
\newcommand{\T}{\top} %Transpose-sign
\renewcommand{\norm}[1]{\left\lvert\left\lvert #1 \right\rvert \right\rvert}  %Norm
\renewcommand{\abs}[1]{\left\lvert #1 \right\rvert} %Absoulute Value
\newcommand{\set}[1]{\left\{ #1 \right\}} %For sets
\newcommand{\ind}[1]{\mathds{1}_{\set{#1}}} %Indicator
\newcommand{\EQC}[2]{\mathbb{E}^{\mathbb{Q}} \left[ #1 \mid #2\right]}
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}} %Adding to equation counter for general enviornment
\newcommand{\pa}[1]{\left( #1 \right)}
\DeclareMathOperator{\VaRa}{\text{VaR}_\alpha}
%\setcounter{section}{0}         %Sets the numbering of sections.
\setcounter{secnumdepth}{0} %Removes the numbers from the sections.
\setlength{\parindent}{0pt}

%For at kunne læse rmd output
%\input{RMD_format.tex}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Introduction}
This report perform an analysis of the of the asset allocation for Best Pensions and provides recommendations as to how the allocation strategy might be improved in order to provide even higher returns for the clients of Best Pension.

The product design in Best Pension currently reflects the high degree of dependence towards providing the promised guarantees at termination of the Target Date Funds (TDF).
Based on the analysis it is strongly recommended to revise the balance between allocation to an active fund and TDF's.
\textcolor{red}{In particular we recommend that Best Pension decreases $L_{target}$ to and converts to a CPPI strategy with multiply of $m$. Further we recommend that Best Pension allows for investments in foreign markets for the active portfolio.}
Further it is advisable to continuously monitor performance in order to maintain a satisfactory level of performance.

In the analysis period the majority of active assets have outperformed investments in zero-coupon-bonds (ZC-bonds) over a 10 year horizon. This is observed in spite of some major down periods for the active assets. However the active in general yield higher returns and are therefore able to recover.
In particular it is observed that the American long-assets have outperformed equivelant European assets. Expanding the investable asset class to allow for investing in foreign markets would therfore significantly have benefited to increase the guarantees of Best Pensions clients.
Based on the analysis we recommend that for the active fund Best Pension invests in the following assets: \textcolor{red}{assets}. The allocation should be based on an \textcolor{red}{strategy}.

Since it is observed that the active assets outperform ZC-bonds an allocation where a higher degree of the initial contribution towards the active fund will in general lead to a larger terminal guarantee for the TDF. As such reducing $L_{target}$ is advisable.
This has become even more relevant as the period of \textit{Quantitative Easening} seems to be over. This means that the original guarantees can be honoured with a much lower initial allocation towards ZC-bonds.
This will in turn mean a higher allocation to the active fund which should yield a higher return and thus a higher terminal guarantee. \newline



This report provides an extensive analysis of allocation strategies for Best Pensions, 
a European pension provider with a strong belief in guarantees. 
Best Pensions offer a series of target date funds, which guarantee the cliets to at 
least get their invested money back.

Due to recent critique of the company's investment strategy, especially
their low allocation towards equity, Best Pensions want to explore more modern approaches
to asset allocation. But they are not willing to deviate from their current product design.

The goal of this report is thus to provide investment advices, which aligns with modern
portfolio theory, while still ensuring that Best Pensions can honour their guarantees.


\section{Recommendations regarding Best Pensions' allocation in their Active Portfolio}
In the following section, we will provide an extensive analysis of the current stock market situation. 
Based on this analysis, we will present our recommendations on, how Best Pensions' should allocate the assets in their Active Portfolio.

\include{FactorAnalysis}

\include{PreliminaryActiveRecom}

\end{document}
